Reconstructing Propositional Proofs in Type Theory

### 2017-10-24 paper/sections/related-work.tex
[ paper ] none inspiration .. :S
[ paper ] related work, first review.

Let us mention a list of some representative of such tools mainly based on the
description by \citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.

The \name{Isabelle} proof assistant has the \name{Sledgehammer} tool.
This program provides a full integration between
automatic theorem provers~\cite{meng2006automation,blanchette2013extending,Fleury2014,hurlin07practical,bohme2010,blanchette2013extending} and
\name{Isabelle/HOL}~\cite{nipkow2002isabelle}, the specialization of
\name{Isabelle} for higher-order logic.
A modular proof-reconstruction workflow is presented jointly with
the full integration of \name{Leo-II} and \name{Satallax} provers with
\name{Isabelle/HOL} in \citeauthor{Een2004}~\cite{Een2004}.

\name{SMTCoq}~\cite{armand2011,Ekici2017} is a tool for the
\name{Coq} proof assistant \cite{coqteam} which provides a certified
checker for proof witness coming from the \SMT solver
\name{veriT}~\cite{bouton2009} and adds a new tactic named verit,
that calls \name{veriT} on any \name{Coq} goal.
In \cite{Bezem2002},
given a fixed but arbitrary first-order signature, the authors
transform a proof produced by the first-order automatic theorem
prover \name{Bliksem} \cite{deNivelle2003} in a \name{Coq} proof
term.

@@

For the proof assistant \Agda, we found two proof-reconstruction tools.
First, the integration with the \name{Waldmeister}~\cite{hillenbrand1997}
prover by \citeauthor{foster2011integrating}~\cite{foster2011integrating}.
A prover for pure equational logic, i.e.
first-order logic with equality but no other predicate symbols and no
functions symbols.
Second, Kanso and Setzer in~\cite{kanso2016light} integrate the propositional
fragment of the \name{EProver}. The tool presented by the authors
translate automatically propositional logic problems written in \Agda
to \TPTP problems. By calling an external wrapper of the \ATP, this
tool gets a \TSTP derivation. The tool parses the \name{EProver}
derivation and outputs \Agda code.

>>>>

% EJEMPLOS DE RECONSTRUCTION DE PRUEBAS USANDO IPTS EN TEORIA DE TIPOS PARA
% ATPS.

% AGDA
% COQ

% Otros: HOL

Many approaches have been proposed for proof-reconstruction and some tools have been
implemented in the last decades.

In type theory, for \Agda and  for the same propositional fragmented used in this paper,
we found the proof-reconstruction proposed by \citeauthor{Kanso2012}
in~\cite{Kanso2012,kanso2016light}. The author present an approach similar to
the reasoning presented in Section~\ref{ssec:workflow}.
Nonetheless, his approach includes semantics reasoning that as we mentioned
in the introduction differs completely from our proof-reconstruction approach.

In \Agda but with another logic, \citeauthor{foster2011integrating}~\cite{foster2011integrating}
describe the proof-reconstruction for \name{Waldmeister}~\cite{hillenbrand1997}
prover to pure equational logic, \ie,
first-order logic with equality but no other predicate symbols and no
functions symbols.

In \name{Coq}~\cite{coqteam}, and proof assistant for type theory like \Agda, 
we found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
certified checker for proof witness coming from the \SMT solver
\name{veriT}~\cite{bouton2009} and adds a new tactic named verit,
that calls \name{veriT} on any \name{Coq} goal.
Also for \name{Coq}, 
given a fixed but arbitrary first-order signature,
\citeauthor{Bezem2002} in \cite{Bezem2002}
transform a proof produced by the first-order automatic theorem
prover \name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof
term.

We found many successful attemps using proof assistant for classical logic
instead of type theory.
Let us mention some representative of such tools. This descriptions is
mainly based on~\citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.

The \name{Isabelle} proof assistant has the \name{Sledgehammer} tool.
This program provides a full integration between
automatic theorem provers~\cite{blanchette2013extending,Fleury2014,bohme2010} and
\name{Isabelle/HOL}~\cite{nipkow2002isabelle}, the specialization of
\name{Isabelle} for higher-order logic.
A modular proof-reconstruction workflow is presented jointly with
the full integration of \name{Leo-II} and \name{Satallax} provers with
\name{Isabelle/HOL} in \citeauthor{Een2004}~\cite{Een2004}.

@@
